
```{r import_harmon_data}

raw_data$Harmon_both_quarter = import.harmon.data() %>%
  construct_countrypair_harmon_index(.,dates_vec = seq.Date(
    from = as.Date(min(raw_data$bis_lbs$Date)),
    to = as.Date(max(raw_data$bis_lbs$Date)),
    by = "quarter") %>% as.yearqtr())

raw_data$Harmon_one_quarter = import.harmon.data() %>%
  construct_countrypair_harmon_index(.,dates_vec = seq.Date(
    from = as.Date(min(raw_data$bis_lbs$Date)),
    to = as.Date(max(raw_data$bis_lbs$Date)),
    by = "quarter") %>% as.yearqtr(),index_status = "one")

```


```{r construct_iv_df}

iv_df = fin_reg_df %>% 
  filter(CountryPair %in%  countries_list$fsap_countries_pairs) %>% 
  left_join(raw_data$Harmon_both_quarter %>% 
              group_by(Date, CountryPair) %>% 
              summarise(Harmon = log(sum(1+Transposed))) %>% 
              ungroup() %>% 
              filter(quarters(Date) == "Q4") %>% 
              mutate(Date = format(Date,"%Y")),
            by = c("Date", "CountryPair"))

```


```{r run_iv_reg}

reg_list$iv_reg =  plm(formula = formula(paste0(reg_formula,
                                                "|.-lag(bank_gdp, 1) + Harmon")),
                       data = iv_df,
                       model = "within",effect = "twoways",
                       index = c("CountryPair","Date"))

```


The Financial Services Action Plan (FSAP) was a package of financial reforms
launched by the EU in 1998 aiming to integrate the EU financial markets and 
reduce the costs of cross-border financial intermediation. The FSAP included 27
EU Directives in banking, capital markets, corporate law, payment systems, and corporate governance. Examples include the Directive on Money Laundering, the Directive on Financial Collateral Arrangements, the Directive on Prospectuses,
and the Directive on Insider Trading and Market Manipulation. EU Directives are
acts that become enforceable only after each EU member country passes domestic legislation adopting the Directive. In practice the legal adoption
(so called transposition into law) of the EU Directives takes several years
and differs considerably across EU member states. Using information  on the
adoption timing of each of the Directives of the FSAP across EU countries, I reconstruct (following @Kalemli-Ozcan2013JF) a bilateral time-varying index that reflects the degree of similarity between the legal-regulatory structures
governing the functioning of financial intermediation across each country pair
in each year.

This index is than used as an instrumental variable in an attempt to mitigate possible endogeneity (such as reversed causation) problem. The results are
presented in table \ref{iv},  all the signs corresponed to signs identified in the main analysis however 


```{r output_iv_reg, include=FALSE}

star_iv = stargazer(reg_list$iv_reg, header = FALSE,digits = 2,
          label = "iv",table.placement = "H",
          title = paste0("Financial synchronization and banking integration: ",
                         "instrumental variable"),
          dep.var.caption = "Fin cycles synch",
          model.numbers = FALSE,
          dep.var.labels.include = FALSE,
          notes = paste0("\\parbox[t]{8cm}{",
                         paste0("The table presents panel estimation that ",
                                "includes twoway fixed effects and country-pair ",
                                " specific linear time trend. ",notes_str_ctrl,
                                "}")),
          notes.align = "l",
          notes.append = FALSE,
          se = list(sqrt(diag(vcovHC(reg_list$iv_reg,cluster = "group")))),
          keep = paste0("^",temp_names,"$"),order = paste0("^",temp_names,"$"),
          covariate.labels = temp_labels,
          omit.stat = c("f","adj.rsq"))

star_iv = sub("\\textit{Note:}  & \\multicolumn{1}{l}{\\parbox[t]{8cm}{",
                    "\\multicolumn{2}{l}{\\parbox[t]{10cm}{\\textit{Note:} ",
                    star_iv,fixed = TRUE)


```


```{r output_iv_table, results="asis"}

cat(star_iv,sep = "\n")

```



