---
title: "Specs Test"
author: "Michael Gurkov"
date: "June 16, 2019"
geometry: margin=2cm
output: pdf_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,echo = FALSE,cache = TRUE,
  message = FALSE,warning = FALSE,comment = "#>"
)
```


```{r load_package}

devtools::load_all()

library(tidyverse)

library(plm)

library(stargazer)
 
library(sandwich)

library(clubSandwich)

library(lmtest)

library(purrr)

```


```{r params_setup}

countries_list = list(
  oecd_countries = c("Australia","Austria","Belgium","Canada","Chile",
                  "Czech_Republic","Denmark","Estonia","Finland","France",
                  "Germany","Greece","Hungary", "Iceland","Ireland",
                  "Israel","Italy","Japan","Korea","Latvia",
                  "Lithuania","Luxembourg","Mexico","Netherlands",
                  "New_Zealand","Norway","Poland","Portugal",
                  "Slovak_Republic","Slovenia","Spain","Sweden",
                  "Switzerland","Turkey","United_Kingdom"
                  ,"United_States"),
  strong_countries = c("Australia","Austria","Belgium","Canada",
                  "Switzerland","Germany","Denmark","Spain",
                  "Finland","France","United_Kingdom","Ireland",
                  "Italy","Japan","Netherlands","Portugal",
                  "Sweden","United_States"),
  fsap_countries = c("Austria","Belgium","Germany","Denmark","Spain",
                   "France","Finland","Greece","Ireland","Italy",
                   "Luxembourg","Netherlands","Portugal",
                   "Sweden","United_Kingdom"))

countries_list$weak_countries = countries_list$oecd_countries[!countries_list$oecd_countries %in% countries_list$strong_countries]


pairs_list = lapply(names(countries_list),
           function(temp_name){
             apply(combn(countries_list[[temp_name]],2), 2,
                   function(temp_col){
                     ifelse(temp_col[1]<temp_col[2],
                            paste(temp_col[1],temp_col[2],sep = "-"),
                            paste(temp_col[2],temp_col[1],sep = "-"))})
  
})

names(pairs_list) = paste(names(countries_list), "pairs", sep = "_")

countries_list = c(countries_list, pairs_list)

rm(pairs_list)

countries_list$cross_country_pairs = countries_list$oecd_countries_pairs[!countries_list$oecd_countries_pairs %in% countries_list$strong_countries_pairs & !countries_list$oecd_countries_pairs %in% countries_list$weak_countries_pairs]

reg_list = list()

control_vars = c("trade_gdp",
           "FX_stab_tot","MI_ind_tot","FO_ind_tot","WGI_tot")

table_names = c("bank_gdp","Crises","bank_gdp:Crises","FD_tot",
                "lag(Fin_synch, 1)","trade_gdp","FX_stab_tot","MI_ind_tot",
                "FO_ind_tot","WGI_tot")

cov_labels = c("Banking linkages",
                 "Crises indicator",
                 "Crises Interaction",
                 "FD indicator",
                 "Fin cycle synch lag",
                 "Trading linkages",
                 "FX stability",
                 "Monetary Independence",
                 "Financial openness",
                 "Governance")


reg_formula = paste("Fin_synch ~ bank_gdp * Crises + FD_tot",
                     "lag(Fin_synch,1)",paste(control_vars, collapse = "+"),
                     sep = "+")

reg_formula_bank_detrended = paste("Fin_synch ~ bank_gdp_detrended * Crises",
                                   "FD_tot",
                                   "lag(Fin_synch,1)",
                                   paste(control_vars, collapse = "+"),
                                   sep = "+")

reg_formula_both_detrended = paste("Fin_synch_detrended ~ bank_gdp_detrended * Crises",
                                   "FD_tot",
                                   "lag(Fin_synch,1)",
                                   paste(control_vars, collapse = "+"),
                                   sep = "+")




```


```{r Import_data}

fin_reg_df_annual = read_rds("C:\\Users\\Misha\\Desktop\\temp_df.rds")

reg_df = fin_reg_df_annual %>% 
    select(c("Date", "CountryPair","Fin_synch_1", "bank_gdp","Crises",
             control_vars,"FD_tot","Time_trend","bank_gdp_detrended",
             "Fin_synch_detrended")) %>% 
  filter(complete.cases(.)) %>% 
  rename(Fin_synch = Fin_synch_1)


```


\section{Fixed effect and time effect estimation}


```{r twoways_estimation}

reg_list$twoways =  make_strata_reg_list(
  countries_list = countries_list,
  reg_df = reg_df,
  reg_formula = formula(reg_formula),my_effect = "twoways")


```


```{r output_twoways, results="asis"}

var_names = names(reg_list$twoways$Strong$coefficients)


temp_ind = sapply(table_names,function(temp_name){
                    which(var_names == temp_name)})


temp_se_list = lapply(reg_list$twoways,function(temp_plm){
                        return(sqrt(diag(vcovHC(temp_plm,cluster = "group"))))
                               })


stargazer(reg_list$twoways, header = FALSE,
          title = "Twoways -  time and country-pair FE",
          dep.var.caption = "Fin cycle synch",
          dep.var.labels.include = FALSE,
          column.labels = gsub("_","-",names(reg_list$twoways)),
          notes = "Clustered standard errors",
          se = temp_se_list,
          order = unlist(temp_ind),
          keep = unlist(temp_ind),
          covariate.labels = cov_labels,
          column.sep.width = "2pt",omit.stat = c("f","adj.rsq"))

rm(temp_se_list, temp_ind, var_names)


```

\newpage


\section{Fixed effect,and linear trend estimation}


```{r individual_lin_trend_estimation}

reg_list$individual_lin_trend =  make_strata_reg_list(
  countries_list = countries_list,
  reg_df = reg_df,
  reg_formula = formula(paste(reg_formula,"Time_trend", sep = "+")),
  my_effect = "individual")


```


```{r output_individual_lin_trend, results="asis"}

temp_reg_list = reg_list$individual_lin_trend

var_names = names(temp_reg_list$Strong$coefficients)


temp_ind = sapply(table_names,function(temp_name){
                    which(var_names == temp_name)})


temp_se_list = lapply(temp_reg_list,
                      function(temp_plm){
                        return(sqrt(diag(vcovHC(temp_plm,cluster = "group"))))
                               })


stargazer(temp_reg_list, header = FALSE,
          title = "Fin synch individual with linear trend",
          dep.var.caption = "Fin cycle synch",
          dep.var.labels.include = FALSE,
          column.labels = gsub("_","-",names(temp_reg_list)),
          notes = "Clustered standard errors",
          se = temp_se_list,
          order = unlist(temp_ind),
          keep = unlist(temp_ind),
          covariate.labels = cov_labels,
          column.sep.width = "2pt",
          omit.stat = c("f","adj.rsq"), 
          add.lines = list(c("Linear trend",
                        rep("Yes", length(temp_reg_list)))))

rm(temp_se_list, temp_ind, var_names, temp_reg_list)


```



\newpage


\section{Fixed effect,time effect and country-pair linear trend estimation}


```{r twoways_lin_trend_estimation}

reg_list$twoways_lin_trend =  make_strata_reg_list(
  countries_list = countries_list,
  reg_df = reg_df,
  reg_formula = formula(paste(reg_formula,"CountryPair:Time_trend", sep = "+")),
  my_effect = "twoways")


```


```{r output_twoways_lin_trend, results="asis"}

var_names = names(reg_list$twoways_lin_trend$Strong$coefficients)


temp_ind = sapply(table_names,function(temp_name){
                    which(var_names == temp_name)})


temp_se_list = lapply(reg_list$twoways_lin_trend,
                      function(temp_plm){
                        return(sqrt(diag(vcovHC(temp_plm,cluster = "group"))))
                               })


stargazer(reg_list$twoways_lin_trend, header = FALSE,
          title = "Fin synch twoways with linear trend",
          dep.var.caption = "Fin cycle synch",
          dep.var.labels.include = FALSE,
          column.labels = gsub("_","-",names(reg_list$twoways_lin_trend)),
          notes = "Clustered standard errors",
          se = temp_se_list,
          order = unlist(temp_ind),
          keep = unlist(temp_ind),
          covariate.labels = cov_labels,
          column.sep.width = "2pt",
          omit.stat = c("f","adj.rsq"), 
          add.lines = list(c("Country-pair linear trend",
                        rep("Yes", length(reg_list$twoways_lin_trend)))))

rm(temp_se_list, temp_ind, var_names)


```


\newpage

\section{Fixed effect,time effect and country-pair robust trend estimation}


```{r twoways_rob_trend_estimation}

reg_list$twoways_rob_trend =  make_strata_reg_list(
  countries_list = countries_list,
  reg_df = reg_df,
  reg_formula = formula(paste(reg_formula,"CountryPair:as.integer(Date)",
                              sep = "+")),
  my_effect = "twoways")


```


```{r output_twoways_rob_trend, results="asis"}

temp_reg_list = reg_list$twoways_rob_trend

var_names = names(temp_reg_list$Strong$coefficients)


temp_ind = sapply(table_names,function(temp_name){
                    which(var_names == temp_name)})


temp_se_list = lapply(temp_reg_list,
                      function(temp_plm){
                        return(sqrt(diag(vcovHC(temp_plm,cluster = "group"))))
                               })


stargazer(temp_reg_list, header = FALSE,
          title = "Fin synch twoways with robust trend",
          dep.var.caption = "Fin cycle synch",
          dep.var.labels.include = FALSE,
          column.labels = gsub("_","-",names(temp_reg_list)),
          notes = "Clustered standard errors",
          se = temp_se_list,
          order = unlist(temp_ind),
          keep = unlist(temp_ind),
          covariate.labels = cov_labels,
          column.sep.width = "2pt",
          omit.stat = c("f","adj.rsq"), 
          add.lines = list(c("Country-pair robust trend",
                        rep("Yes", length(temp_reg_list)))))

rm(temp_se_list, temp_ind, var_names,temp_reg_list)


```


\newpage

\section{Fixed effect,time effect and detrended bank}


```{r twoway_bank_detrend_estimation}

reg_list$twoway_bank_detrend =  make_strata_reg_list(
  countries_list = countries_list,
  reg_df = reg_df,
  reg_formula = formula(reg_formula_bank_detrended),
  my_effect = "twoways")


```


```{r output_twoway_bank_detrend, results="asis"}

var_names = names(reg_list$twoway_bank_detrend$Strong$coefficients)


temp_ind = sapply(gsub("bank_gdp","bank_gdp_detrended",table_names),
                  function(temp_name){
                    which(var_names == temp_name)})


temp_se_list = lapply(reg_list$twoway_bank_detrend,
                      function(temp_plm){
                        return(sqrt(diag(vcovHC(temp_plm,cluster = "group"))))
                               })


stargazer(reg_list$twoway_bank_detrend, header = FALSE,
          title = "Fin synch twoway with detrended banking",
          dep.var.caption = "Fin cycle synch",
          dep.var.labels.include = FALSE,
          column.labels = gsub("_","-",names(reg_list$twoway_bank_detrend)),
          notes = "Clustered standard errors",
          se = temp_se_list,
          order = unlist(temp_ind),
          keep = unlist(temp_ind),
          covariate.labels = gsub("Banking linkages","Banking linkages (detrended)",
                                  cov_labels),
          column.sep.width = "2pt",omit.stat = c("f","adj.rsq"))

rm(temp_se_list, temp_ind, var_names)


```



\section{Fixed effect,time effect and detrended bank, linear trend}


```{r twoway_bank_detrend_lin_trend_estimation}

reg_list$twoway_bank_detrend_lin_trend =  make_strata_reg_list(
  countries_list = countries_list,
  reg_df = reg_df,
  reg_formula = formula(paste(reg_formula_bank_detrended,
                              "CountryPair:Time_trend", sep = "+")),
  my_effect = "twoways")


```


```{r output_twoway_bank_detrend_lin_trend, results="asis"}

var_names = names(reg_list$twoway_bank_detrend_lin_trend$Strong$coefficients)

temp_ind = sapply(gsub("bank_gdp","bank_gdp_detrended",table_names),
                  function(temp_name){
                    which(var_names == temp_name)})


temp_se_list = lapply(reg_list$twoway_bank_detrend_lin_trend,
                      function(temp_plm){
                        return(sqrt(diag(vcovHC(temp_plm,cluster = "group"))))
                               })


stargazer(reg_list$twoway_bank_detrend_lin_trend, header = FALSE,
          title = "Twoway with detrended banking and linear trend",
          dep.var.caption = "Fin cycle synch",
          dep.var.labels.include = FALSE,
          column.labels = gsub("_","-",names(reg_list$twoway_bank_detrend_lin_trend)),
          notes = "Clustered standard errors",
          se = temp_se_list,
          order = unlist(temp_ind),
          keep = unlist(temp_ind),
          covariate.labels = gsub("Banking linkages",
                                  "Banking linkages (detrended)",
                                  cov_labels),
          column.sep.width = "2pt",omit.stat = c("f","adj.rsq"), 
          add.lines = list(c("Country-pair linear trend",
                        rep("Yes", length(reg_list$twoways_lin_trend)))))

rm(temp_se_list, temp_ind, var_names)


```


\newpage

\section{Fixed effect,time effect and detrended bank, robust trend}


```{r twoway_bank_detrend_rob_trend_estimation}

reg_list$twoway_bank_detrend_rob_trend =  make_strata_reg_list(
  countries_list = countries_list,
  reg_df = reg_df,
  reg_formula = formula(paste(reg_formula_bank_detrended,
                              "CountryPair:as.integer(Date)", sep = "+")),
  my_effect = "twoways")


```


```{r output_twoway_bank_detrend_rob_trend, results="asis"}

var_names = names(reg_list$twoway_bank_detrend_rob_trend$Strong$coefficients)

temp_ind = sapply(gsub("bank_gdp","bank_gdp_detrended",table_names),
                  function(temp_name){
                    which(var_names == temp_name)})


temp_se_list = lapply(reg_list$twoway_bank_detrend_rob_trend,
                      function(temp_plm){
                        return(sqrt(diag(vcovHC(temp_plm,cluster = "group"))))
                               })


stargazer(reg_list$twoway_bank_detrend_rob_trend, header = FALSE,
          title = "Twoway with detrended banking and robust trend",
          dep.var.caption = "Fin cycle synch",
          dep.var.labels.include = FALSE,
          column.labels = gsub("_","-",
                               names(reg_list$twoway_bank_detrend_rob_trend)),
          notes = "Clustered standard errors",
          se = temp_se_list,
          order = unlist(temp_ind),
          keep = unlist(temp_ind),
          covariate.labels = gsub("Banking linkages",
                                  "Banking linkages (detrended)",
                                  cov_labels),
          column.sep.width = "2pt",omit.stat = c("f","adj.rsq"), 
          add.lines = list(c("Country-pair robust trend",
                        rep("Yes", length(reg_list$twoways_lin_trend)))))

rm(temp_se_list, temp_ind, var_names)


```


\newpage

\section{Fixed effect,time effect, detrended bank and detrended fin synch}


```{r twoway_both_detrend_estimation}


reg_list$twoway_both_detrend =  make_strata_reg_list(
  countries_list = countries_list,
  reg_df = reg_df,
  reg_formula = formula(reg_formula_both_detrended),
  my_effect = "twoways")




```


```{r output_twoway_both_detrend, results="asis"}

var_names = names(reg_list$twoway_both_detrend$Strong$coefficients)

temp_ind = sapply(gsub("Fin_synch","Fin_synch_detrended",
                       gsub("bank_gdp","bank_gdp_detrended",
                            table_names)),function(temp_name){
                    which(var_names == temp_name)})


temp_se_list = lapply(reg_list$twoway_both_detrend,
                      function(temp_plm){
                        return(sqrt(diag(vcovHC(temp_plm,cluster = "group"))))
                               })


stargazer(reg_list$twoway_both_detrend, header = FALSE,
          title = "Twoways both detrended",
          dep.var.caption = "Fin cycle synch",
          dep.var.labels.include = FALSE,
          column.labels = gsub("_","-",names(reg_list$twoway_both_detrend)),
          notes = "Clustered standard errors",
          se = temp_se_list,
          order = unlist(temp_ind),
          keep = unlist(temp_ind),
          covariate.labels = cov_labels,
          column.sep.width = "2pt",omit.stat = c("f","adj.rsq"))

rm(temp_se_list, temp_ind, var_names)


```

