---
title: "Financial Cycle synchronization and cross border credit"
institute: "Bank of Israel \\newline Research Department, Finance Division"
author: "Michael Gurkov"
# date: "August 15, 2018"
classoption: t
output:
  beamer_presentation:
    keep_tex: true
    includes:
      in_header: GlobalFinCyclePreamble.tex
    latex_engine: xelatex
vignette: >
  %\VignetteIndexEntry{GlobalFinCycle-Presentation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,echo = FALSE,message = FALSE,warning = FALSE,
  comment = "#>"
)
```


```{r load_package}

devtools::load_all()

library(ggplot2)

library(stargazer)


```


```{r Import_dataset,cache = TRUE}

params_list = make.params.list()

dataset = import_dataset()

```


```{r fin_reg_calculate,cache = TRUE}

fin_reg_list = lapply(list(NULL,
                           params_list$strong_countries_pairs,
                           params_list$weak_countries_pairs,
                           params_list$cross_country_pairs,
                           c(params_list$cross_country_pairs,
                             params_list$weak_countries_pairs)),
                      function(temp_vec){
                        
                        form = formula(Fin_ret ~ bank_gdp + trade_gdp +
                                                FO_ind_tot + FX_stab_avg + 
                                                FD_avg + MI_ind_tot)
                        
                        reg_df = dataset$fin_reg_df %>% 
                          {if(!is.null(temp_vec)) filter(.,CountryPair %in%
                                                           temp_vec) else .}

                        temp_reg = plm(formula = form,
                            model = "within",effect = "twoways",
                            data = reg_df,
                            index = c("CountryPair","Date"))
                        
                        return(temp_reg)
                        
                        })


```


```{r within_reg, results="asis",cache = TRUE}

within_reg_list = lapply(list(NULL,
                           params_list$strong_countries_pairs,
                           params_list$weak_countries_pairs,
                           params_list$cross_country_pairs,
                           c(params_list$cross_country_pairs,
                             params_list$weak_countries_pairs)),
                      function(temp_vec){
                        
                        form = formula(Fin_ret ~ bank_gdp)
                        
                        reg_df = dataset$fin_reg_df %>% 
                          {if(!is.null(temp_vec)) filter(.,CountryPair %in%
                                                           temp_vec) else .}

                        temp_reg = plm(formula = form,
                            model = "within",effect = "twoways",
                            data = reg_df, index = c("CountryPair","Date"))
                        
                        return(temp_reg)
                        
                        })



panel_reg_list_pooling = lapply(list(NULL,
                           params_list$strong_countries_pairs,
                           params_list$weak_countries_pairs,
                           params_list$cross_country_pairs,
                           c(params_list$cross_country_pairs,
                             params_list$weak_countries_pairs)),
                      function(temp_vec){
                        
                        form = formula(Fin_ret ~ bank_gdp)
                        
                        reg_df = dataset$fin_reg_df %>% 
                          {if(!is.null(temp_vec)) filter(.,CountryPair %in%
                                                           temp_vec) else .}

                        temp_reg = plm(formula = form,
                            model = "pooling",
                            data = reg_df, index = c("CountryPair","Date"))
                        
                        return(temp_reg)
                        
                        })


panel_reg_list_time_FE = lapply(list(NULL,
                           params_list$strong_countries_pairs,
                           params_list$weak_countries_pairs,
                           params_list$cross_country_pairs,
                           c(params_list$cross_country_pairs,
                             params_list$weak_countries_pairs)),
                      function(temp_vec){
                        
                        form = formula(Fin_ret ~ bank_gdp)
                        
                        reg_df = dataset$fin_reg_df %>% 
                          {if(!is.null(temp_vec)) filter(.,CountryPair %in%
                                                           temp_vec) else .}

                        temp_reg = plm(formula = form,
                            model = "within",effect = "time",
                            data = reg_df, index = c("CountryPair","Date"))
                        
                        return(temp_reg)
                        
                        })



panel_reg_list_countrypair_FE = lapply(list(NULL,
                           params_list$strong_countries_pairs,
                           params_list$weak_countries_pairs,
                           params_list$cross_country_pairs,
                           c(params_list$cross_country_pairs,
                             params_list$weak_countries_pairs)),
                      function(temp_vec){
                        
                        form = formula(Fin_ret ~ bank_gdp)
                        
                        reg_df = dataset$fin_reg_df %>% 
                          {if(!is.null(temp_vec)) filter(.,CountryPair %in%
                                                           temp_vec) else .}

                        temp_reg = plm(formula = form,
                            model = "within",effect = "individual",
                            data = reg_df, index = c("CountryPair","Date"))
                        
                        return(temp_reg)
                        
                        })




```

# Motivation

\begin{itemize}

\setlength\itemsep{1.5em}

  \item
  Kalemi-Ozcan et all (Journal of Finance, 2013) find \textbf{negative}
  association between financial integration and business cycles synchronization

  \item
  The authors use data of 18 ("strong OECD" such as Australia,Sweden,
  United Kingdom, etc..) countries for 1978-2006 period.
  They construct panel of 153 country pairs in each year.

  \item
  Possible economic mechanism: money moves from bad productivity shock to other   places and that results productivity divergency

\end{itemize}





# Motivation

The general finding is \textbf{negative} association between financial integration and business cycles synchronization


\begin{itemize}

\setlength\itemsep{2em}

  \item
  The \textit{cross country} (between model) association is significantly
  \textit{positive}.

  \item
  The \textit{panel} (within model with time and country pair fixed effects)
  association is significantly \textit{negative}.

  \item
  Authors suggest that common global time shocks and specific country pair characterisitcs explain the difference

\end{itemize}




# Financial Cycle - Cross country Scatter plot

```{r plot_between_model}

ggplot(dataset$fin_reg_df %>% 
         select(CountryPair, Fin_ret, bank_gdp) %>% 
         group_by(CountryPair) %>% 
         summarise_all(.,.funs = list(.~mean), na.rm = TRUE),
       aes(x = bank_gdp, y = Fin_ret * 100,
           color = ifelse(CountryPair %in% params_list$strong_countries_pairs,
                         "\"Strong\" countrypairs","Other"))) + 
  geom_point() + 
  geom_smooth(method = "lm",se = FALSE) +
  theme_bw() + 
  labs(title = paste0("Average synchronization of financial growth rates",
                      "\n (Between countrypairs)"),
       y = "Growth rate negative difference (percent)",
       x = "Cross border bank balance to gdp") + 
  theme(plot.title = element_text(hjust = 0.5, size = 25),
        legend.position = "bottom",
        legend.title = element_blank(),
        axis.text = element_text(size = 20),
        legend.text = element_text(size = 20))


```



# Financial Cycle - Panel data Scatter plot

```{r, cache=TRUE}

temp_df = dataset$fin_reg_df %>% 
  select(CountryPair,Date,Fin_ret,bank_gdp) %>% 
  ungroup() %>% 
  filter(complete.cases(.))

clean_df = data.frame(Fin_Res = lm(Fin_ret~factor(CountryPair) + factor(Date), data = temp_df)$residuals,Bank_Res = lm(bank_gdp~factor(CountryPair) + factor(Date), data = temp_df)$residuals)

clean_df = cbind.data.frame(clean_df, temp_df %>% 
                              select(CountryPair, Date))

  
```


```{r plot_within_model}

ggplot(clean_df, aes(x = Bank_Res, y = Fin_Res,
                     color = ifelse(CountryPair %in%
                                      params_list$strong_countries_pairs,
                         "\"Strong\" countrypairs","Other"))) + 
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE) + 
  labs(title = paste0("Average synchronization of financial growth rates",
                      "\n (Within countrypairs,",
                      " netting time and country pair fixed effects)"),
       y = "Growth rate negative difference (percent)",
       x = "Cross border bank balance to gdp") + 
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5, size = 25),
        legend.position = "bottom",
        legend.title = element_blank(),
        axis.text = element_text(size = 20),
        legend.text = element_text(size = 20))


```



# Financial Cycle - Cross country

```{r between_reg, results="asis",cache = TRUE}

between_reg_list = lapply(list(NULL,
                           params_list$strong_countries_pairs,
                           params_list$weak_countries_pairs,
                           params_list$cross_country_pairs,
                           c(params_list$cross_country_pairs,
                             params_list$weak_countries_pairs)),
                      function(temp_vec){
                        
                        form = formula(Fin_ret ~ bank_gdp)
                        
                        reg_df = dataset$fin_reg_df %>% 
                          {if(!is.null(temp_vec)) filter(.,CountryPair %in%
                                                           temp_vec) else .}

                        temp_reg = plm(formula = form,
                            model = "between",data = reg_df,
                            index = c("CountryPair","Date"))
                        
                        return(temp_reg)
                        
                        })


stargazer(between_reg_list, header = FALSE,
          dep.var.labels = rep("",5),
          dep.var.caption = "Credit cycle synchronization",
          column.labels = c("All","Strong","Weak","Cross","Cross and Weak"),
          omit.stat = c("f","adj.rsq"), font.size = "scriptsize",
          report = "vc*", title = "Cross country averages",
          omit.table.layout = paste0("-","=","-!","=!","a", collapse = ""))


```




# Financial Cycle - Panel data

```{r table_within_FE, results="asis"}

stargazer(within_reg_list, header = FALSE,
          dep.var.labels = rep("",5),
          dep.var.caption = "Credit cycle synchronization",
          column.labels = c("All","Strong","Weak","Cross","Cross and Weak"),
          omit.stat = c("f","adj.rsq"), font.size = "scriptsize",
          report = "vc*",title = "Panel fixed effect time and country pair",
          omit.table.layout = paste0("-","=","-!","=!","a", collapse = ""))


```








# Financial Cycle Regressions

```{r, results="asis",cache = TRUE}

stargazer(fin_reg_list, header = FALSE,
          dep.var.labels = rep("",5),
          dep.var.caption = "Credit cycle synchronization",
          column.labels = c("All","Strong","Weak","Cross","Cross and Weak"),
          omit.stat = c("f","adj.rsq"), font.size = "scriptsize",
          report = "vc*",title = "Panel regression with controls and fixed effects",
          omit.table.layout = paste0("-","=","-!","=!","a", collapse = ""))


```




# Summary Statistics
```{r summary_stat}


ggplot(dataset$fin_reg_df %>% 
         as.data.frame() %>% 
         mutate(G = ifelse(CountryPair %in% params_list$strong_countries_pairs,
                           "\"Strong\" countrypairs","Other")) %>% 
         group_by(G) %>% 
         summarise_at(.,.vars = vars(FD_avg,FO_ind_tot,FX_stab_avg,MI_ind_tot),
                      .funs = list(~mean(., na.rm = TRUE))) %>% 
         gather(key = Indicator, value = Val, -G),
       aes(x = Indicator, y = Val, group = G, fill = G)) + 
  geom_bar(stat = "identity", position = "dodge") + 
  # scale_x_discrete(labels = rep("A",4)) + 
  labs(title = "Controls comparison", y = "", x = "") + 
  theme_bw() + 
  theme(legend.position = "bottom",legend.title = element_blank(),
        plot.title = element_text(hjust = 0.5),
        legend.spacing.x = unit(10, "pt"))



```

# Financial Cycle - Panel data

```{r table_within_pooling, results="asis"}

stargazer(panel_reg_list_pooling, header = FALSE,
          dep.var.labels = rep("",5),
          dep.var.caption = "Credit cycle synchronization",
          column.labels = c("All","Strong","Weak","Cross","Cross and Weak"),
          omit.stat = c("f","adj.rsq"), font.size = "scriptsize",
          report = "vc*",title = "Panel Pooling",
          omit.table.layout = paste0("-","=","-!","=!","a", collapse = ""))


```







# Financial Cycle - Panel data

```{r table_within_time_FE, results="asis"}

stargazer(panel_reg_list_time_FE, header = FALSE,
          dep.var.labels = rep("",5),
          dep.var.caption = "Credit cycle synchronization",
          column.labels = c("All","Strong","Weak","Cross","Cross and Weak"),
          omit.stat = c("f","adj.rsq"), font.size = "scriptsize",
          report = "vc*",title = "Panel fixed effect time",
          omit.table.layout = paste0("-","=","-!","=!","a", collapse = ""))


```







# Financial Cycle - Panel data

```{r table_within_countrypairFE, results="asis"}

stargazer(panel_reg_list_countrypair_FE, header = FALSE,
          dep.var.labels = rep("",5),
          dep.var.caption = "Credit cycle synchronization",
          column.labels = c("All","Strong","Weak","Cross","Cross and Weak"),
          omit.stat = c("f","adj.rsq"), font.size = "scriptsize",
          report = "vc*",title = "Panel fixed effect country pair",
          omit.table.layout = paste0("-","=","-!","=!","a", collapse = ""))


```









